\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
}

% opening here
\opening{To the Smart Scholarship Selection Committee:}
\raggedright % if you like this sort of thing
\setlength{\parindent}{15pt} % if you like this sort of thing

I am happy to recommend Jocelyne Yataco for your program. Jocelyne was a student in my department and was in two classes I taught in, EW200 (Introduction to Systems Engineering) and EW202 (Principles of Mechatronics). These two classes are taught to all Robotics and Controls Engineering majors during their 3/c (sophomore) year here at the Naval Academy and cover programming, engineering design, and embedded microcontrollers.  

I remember vividly interacting with Jocelyne when she came on several occasions for extra instruction. In EW200, she worked hard to learn objected-oriented programming principles applied to graphical user interfaces (GUI) in Matlab, even though the rudimentary ``video game'' project she was assigned only required very basic plotting commands. I also distinctly remember her keeping me on my toes at exam reviews for EW200 and EW202, where she would attend and ask very insightful questions about C programming, basic circuits, embedded microcontrollers, servos, and motors. 

Jocelyne was slated to be in my section for EW485 (Comparative Biomechanics) this year. I was very sad when I saw her name dropped from my class list, due to medical reasons that are requiring her to leave the Naval Academy. I wish I could work more with this outstanding student, and I know she will find great success in your program and wherever she goes next. 

%Maybe you could talk about the time I came for EI for my ES200 project where I was working on how to save data on GUI for my video game score menu. I’m asking letters from Capt Campbell, my leadership professor, and Ms. Julia Grim, the study abroad coordinator.


\closing{Very respectfully,} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}