\documentclass[12pt]{wrceletter}

%
%Thank you very much. My major is Electrical Engineering and I am applying to the Advance Cybersecurity Experience for Students Honors minor. (ACES)
%
%Here is the recommendation link for ACES: 
%https://go.umd.edu/acesminorletterofrec
%
%
%Lockheed Martin scholarship should be sending you the recommendation link.
%
%
%I currently have an internship for summer 2020 with the Army Research Lab to work in a night vision research project. I have also applied for the Artificial Intelligence and Machine Learning 2020 summer internship with the ICAI2 program here at UMD. I am also applying to have an internship with the CIA for the summer 2021. I would like to work for the Department of Defense after I graduate.
%
%I am involved in many student groups. I am subscribed in the email lists for Women in Engineering, Minorities in Engineering, and Veterans and Military affiliated students. I am also planning on joining the Black Belt, Triathlon, Scuba diving, jogging, Latin dance, gymnastics and the Terrapin Trail club. For my academic goals, have joined the Electrical Engineering club, Robotics club, cyber security club, and Society of American Military Engineers (SAME) club. I am going to apply to become the SAME club president for next semester since the current president is graduating.
%
%Thank you very much.
%
%Very respectfully,
%
%
%
%Jocelyne Yataco



\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
}

% opening here
\opening{To the Lockheed Martin Scholarship Selection Committee:}
\raggedright % if you like this sort of thing
\setlength{\parindent}{15pt} % if you like this sort of thing

I am happy to recommend Jocelyne Yataco for your program. Jocelyne was a student in my department and was in two classes I taught in, EW200 (Introduction to Systems Engineering) and EW202 (Principles of Mechatronics). These two classes are taught to all Robotics and Controls Engineering majors during their 3/c (sophomore) year here at the Naval Academy and cover programming, engineering design, and embedded microcontrollers. Our majors apply their robotics and controls engineering abilities in all manner of manufacturing engineering situations.   

I remember vividly interacting with Jocelyne when she came on several occasions for extra instruction. In EW200, she worked hard to learn objected-oriented programming principles applied to graphical user interfaces (GUI) in Matlab, even though the rudimentary ``video game'' project she was assigned only required very basic plotting commands. I also distinctly remember her keeping me on my toes at exam reviews for EW200 and EW202, where she would attend and ask very insightful questions about C programming, basic circuits, embedded microcontrollers, servos, and motors. 

Jocelyne was slated to be in my section for EW485 (Comparative Biomechanics) this year. I was very sad when I saw her name dropped from my class list, due to medical reasons that are requiring her to leave the Naval Academy. I understand she is thriving as an electrical engineering major at UMD. I wish I could work more with this outstanding student, and I know she will find great success with the help of a Lockhed Martin scholarship.

%Maybe you could talk about the time I came for EI for my ES200 project where I was working on how to save data on GUI for my video game score menu. I’m asking letters from Capt Campbell, my leadership professor, and Ms. Julia Grim, the study abroad coordinator.


\closing{Very respectfully,} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}